
%\uppercase{Kickff helps reduce labor cost by providing a safe developer layoff solution for software companies.}
\subsection*{Concordia University,November 19, 2014}
A group of Concordia University students have developed a software application called Kickoff to help software companies control their labor cost. Based on the desired salary cut off amount, it can give out a programmer layoff list that is the least harmful to the software project and an abandoned source code take over solution.

Laying  off developer is dangerous to software companies. Since the part of project files maintained only by the layoff developers will become unknown to the company. If there was a bug reported in those files, nothing could be done until the remain developers learned how to maintain them. The learning process is time consuming, but the customer may select other product if the bug could not be fixed in a short time.  

However, In order to survive in a critical financial situation, software companies sometimes have to lay off developers to reduce the labor cost. Laying off senior developers cuts off more cost but lose more project files than laying off junior developers. Therefore deciding the layoff solution is difficult for software companies.

Kickoff first generates a set of possible solutions according to the target cutoff cost, then applies the "Optimized Truck Factor" algorithm to find out the least harmful solution and uses the "candidate finding system" to generate the project remedy solution. 

With Kickoff, it is easier for a software company to cut off their labor cost.  




