%need to use \usepackage{amsmath,amssymb,amsthm,mathrsfs,amsfonts,dsfont}
\section{The Optimized TF Algorithm}
TODO:re-write: The `truck factor' is a measure in the agile community of the number of
developers that must leave (\eg get hit by a truck) before the project
fails~\cite{Torchiano2011Wetsom}. Previous work has calculated the maximum number of files
that are lost when a group of developers leave. Since this calculation has a
$O(n!)$, they are able to examine only small projects at one single point in time.
We contribute a stoping condition that allows us to calculate the maximum loss
quickly, so that we can examine the truck factor on large projects. We prove
that we attain the optimal solution and show how the truck factor for Chrome and
Linux changes over time. We compare the maximum loss to the actual loss that
Chrome and Linux have experienced suggesting how likely they are to suffer from
similar turnover events.
\subsubsection{Limitation of The Naive TF Algorithm}
The naive TF algorithm proposed by Ricca \etal \cite{Ricca2011PROFES} has a high time complexicy.
When $n$ is the size of developer team and $m$ is the total number of files in the project then the time complexity is given by:
\begin{equation}T(n,m) = n*\sum_{i=1}^n \frac{n!}{i!(n-i)!}*m\end{equation}
For example, if a project has 30 developers then the number of developer combinations that is over 17 million.
In previous work, the largest project had only 38 developers
\cite{Torchiano2011Wetsom}. We are considering much larger projects, for
example, Chrome and Linux have 1000's of contributors. It is impractical to
combute all developer combination.
We introduce a stopping condition which we prove identifies, for a given group size, the set of developers who's loss will result in the maximum file loss.
\subsubsection{Truck factor definitions}
The following is the definisiton of symbols which will be used later:\\
$D =$ the set of all developers in the project.\\ %and $|D|$= the size of set $D$, in other words it is the total number of developers in the project.\\
$d_{i}=$ a particula develoer in $D$, $i$ is the ID of the developer.\\
$F=$ the set of all files in the project.\\ %then $|F|$= total number of files in the project. \\
$f_{j}=$a particula file in $F$, $j$ is the ID of it.\\
$M(f_{j})=$ the set of develoers who have modified the file $f_{j}$.\\
$I()$ is the logic function defined as:
\[ I(condition) = \left\{
\begin{array}{l l}
1 & \textmd{if condition is true}\\
0 & \textmd{otherwise}
\end{array} \right.\]
We first calculate the proportion of developer $d_{i}$ who have modified the file $f_{j}$ by equation:
\begin{equation}L(d_{i},f_{j})=\frac{1}{|M(f_{j})|} * I(d_{i} \in M(f_{j} )) \end{equation}
Then the file loss (FL) function returns how many files would be abandoned if a given developer combination $C$ left the project:
\begin{equation}
FL(C) = \sum_{d_i \in C} \sum_{f_i \in F} (I(M(f_i) \subseteq C)* L(d_i,f_i))
\end{equation}
Then the maximum file loss for a given group size is returned by the truck factor function:
$TF(C) = max(FL(C))$
We can see that a naive implementation of this algorithm will have a complexity of $O(n!)$, which is impractical to compute for large projects.
\subsubsection{Stopping Condition}
The shared proportion of the number of files a developer $d_i$ has modified on the project:
\begin{equation} L(d_i) = \sum_{f_i \in F} L(d_{i},f_{j}) \end{equation}
The upper bound of the file loss for a given developer combination $C$ is:
\begin{equation} UFL(C) = \sum_{d_i \in C}L(d_i) \end{equation}
Since \[\forall condition: I(condition) \leq 1 \]
We have:
\begin{equation} FL(C) \leq \sum_{d_i \in C} \sum_{f_i \in F} [1 * L(d_i,f_i)] = UFL(C)\end{equation}
%We have:
%\begin{equation}
%\forall C:FL(C)\leq UFL(C)
%\end{equation}
For each group size, we order the developer combinations by their $UFL$ value and calculate the $FL$ for each developer combination until the stopping condition, $UFL(C)<max(FL)$ is met.
In other words, we have shown that the number of files that a given group of developers modify, $UFL$, will be less than or equal to the number of files that these developers own exclusively, $FL$. Provided that we order the developers by the number of files that they modify, $UFL$, we can stop when the maximum loss that we calculated from the $FL$ function is greater than or equal to the total number of files that the subsequent group of developers modify. The algorithm is presented in Box?Algorithm
\subsubsection{TODO:combinations}
Unforetunately, we still must calculate must do $n!$ $UFL$ calculations. So we introduce a method to order these $UFL$ calculations.
TODO
\begin{algorithm}
\SetAlgoLined
\SetKwData{$d_i$}{$d_i$}\SetKwData{$F$}{$F$}
\SetKwFunction{K}{K}\SetKwFunction{KL}{KL}\SetKwFunction{SF}{SF}
\end{algorithm}
\begin{raggedright}
\scriptsize
$TFX = threashold$,$i=1$;\\
$F=$total number of files in the project;\\
For each developer $d_i$ in the team $D$, calculate $K(d_i)$;\\
Order $D$ by $K(d_i)$ descently;\\
While $i\leq |D|$ repeat the block\{\\
$Max\_fileLoss =0$;\\
$combination\_generating(D,i)$;\\
Initialize $input\_combination = input\_flow\_generating()$;\\
While $SF(input\_combination)\geq Max\_fileLoss$ repeat the block\{\\
If $KL(input\_combination) > Max\_fileLoss$ is true, $Max\_fileLoss=KL(input\_combination)$
$input\_combination = input\_flow\_generating()$;\\
\}\\
out print: if you lost a developer combination of size $size$, your maximum file loss would be $Max\_fileLoss$;\\
if $Max\_fileLoss \geq (TFX*F)$ is true the Truck Factor is $size$ and stop the algorithm;\\
Otherwise increase $i$ by 1 and continue;\\
\}\\
\end{raggedright}
\subsubsection{Distribution of developer ownership}
In the worst case, the files are uniformly distributed among the developement
team and each developer modifies a similar number of files. In this case, to
calculate the maximum file loss, we need to cacluate all combinations of
developers, which is $O(n!)$. However, as we can see in Figure
~\ref{figFilesTouched}, the distribution is heavly skewed towards developers
that modify a very small number of files, so the stopping condition is triggered
early. For Linux, in the median case, a developer modifies only 6 files, and at
the \nth{80} percentile a developers modifies 33 files. In contrast, there are
51 developers above the \nth{99} percentile, who modify at least 680 files each.
The maximimum number of files a developer modifies is 4.4k.
When we run our algorithm on the most recent version of Linux, which has 3784
developesr and 30k files, up to a group size of 30, we have to perform only
4049 $FL$
%2012 | 3 | 4049
Our algorithm makes computing the truck factor practical on very large projects.




