%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cies Resume/CV
% LaTeX Template
% Version 1.1 (20/7/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)

\include{structure} % Include structure.tex which contains packages and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\maintitle{Yuecai Zhu}{August 4, 1983}  % Your name and date of birth or subtitle

\noindent\href{mailto:zhuyuecai@gmail.com}{zhuyuecai@gmail.com}\bull % Your email address
\textsmaller{+}1 (438) 345-7638\bull 
%smith01 \textit{(Skype)}\bull % Your phone number(s) and Skype username
%\href{http://www.johnsmith.com}{www.johnsmith.com}\\ % Your URL
3305 De Rouen \bull Montreal, H1W 1L2\bull Quebec\bull Canada % Your address

\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\roottitle{Summary} % Root section title

\vspace{-1.3em} % Reduce whitespace after the Summary heading and the two-column content

\begin{multicols}{2}  % Start a two-column layout
\noindent \textit{A summary of your interests, achievements, history, topic of study or any other short summary of your professional life.}\\\\
I have excellent knowledge of different statistic models and categorical analysis models. I am working as a research assistant for professor Peter C. Rigby in Concordia University. My responsibility is to try different statistic models to build math model for a given data sample ,design and implement new algorithm for research projects.  

I am also an experienced Java and Python programmer with strong database and scripting skill.  I studied Java in university, at the same time I studied Python by self. When I worked as an IT analyst in Hydro One, I scripted with Python to perform data computation. And now my daily task is to script with Python and SQL to perform data computation. Moreover, I implemented the optimized Truck Factor algorithm with Python and SQL for the paper 'Developer Turnover and Succession: Empirical studies of the susceptibility and damage from developer turnover'. 

Moreover, I have over 3 years of experience working in the banking industry, 2 years of experience in finance derivative investment. During the launch of the 'Online Declaration System', I made a concrete action plan, communicated with sub-branches and helped them finished the task. I'm a team player who values communication and cooperation with colleagues. 
\end{multicols}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Experience} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.intellecap.com}{Intellecap}/\href{http://istpl.in}{\acr{ISTPL}}}
{\textsc{Mumbai, Pune \& Hyderabad, India}} {

\headedsubsection % Job title entry for the current employer
{\acr{IT} Consultant}
{Nov '08 -- Feb '09}
{\bodytext{Intellecap is a social-sector advisory firm serving corporates, non-profits, development agencies and governments working in developing markets. I assessed their software development team and methodologies, trained their developers and build several web applications. One of those apps is \href{http://www.mostfit.org}{Mostfit}, an open source \acr{MIS} for \href{http://en.wikipedia.org/wiki/Microcredit}{microcredit} lenders.}}

\headedsubsection % Job title entry for the current employer
{\acr{IT} \& Strategy Consultant}
{Jan '10 -- Aug '11}
{\bodytext{\href{http://www.mostfit.org}{Mostfit} became a success and I was called in to solve several technical challenges, look at potential growth strategies, and assist in making a business case for this product in a company of its own.}}

\headedsubsection % Job title entry for the current employer
{Chief Technology Officer}
{Oct '11 -- present}
{\bodytext{Joined the \acr{C}-family to make \href{http://www.mostfit.org}{Mostfit} the nr.1 software solution for micro credit lenders around the globe.}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.dharmapublishing.com}{Dharma Publishing}}
{\textsc{near San Francisco (\acr{CA}), \acr{USA}}} {

\headedsubsection % Job title entry for the current employer
{\acr{IT} Consultant}
{Nov '09 -- Dec '09}
{\bodytext{Dharma Publishing, the worlds largest Buddhist publisher, is a non-profit, all-volunteer organization that helps to preserve Tibetan Buddhism and culture. I build them a \href{http://www.dharmapublishing.com}{web store}, and moved the infrastructure of all their web media to a nearly zero maintenance setup that they can maintain themselves.}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.kde.org}{KDE}}
{\href{http://edu.kde.org/kturtle}{edu.kde.org/kturtle}} {

\headedsubsection % Job title entry for the current employer
{Software Engineer}
{Dec '03 -- present}
{\bodytext{KTurtle is an educational programming environment that simplifies learning the basics of programming. At early age I learned programming using \acr{MSX-LOGO}, by creating KTurtle I want to ensure future generation's access to a similar piece of software. I was honored when KTurtle got admitted to \acr{KDE} in 2003.}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://truetopiaproject.org}{Truetopia Project}}
{\href{http://truetopiaproject.org}{truetopiaproject.org}} {

\headedsubsection % Job title entry for the current employer
{Initiator}
{Nov '07 -- Apr '10}
{\bodytext{The Truetopia Project is an open source web application (Rails) to facilitate self-governing communities. It provides a workflow for collaborative problem identification and solution design.}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.opendream.th}{Opendream}}
{\textsc{Bangkok, Thailand}} {

\headedsubsection % Job title entry for the current employer
{\acr{IT} Consultant}
{Aug '09 -- Sep '09}
{\bodytext{Architected and largely implemented an open source media sharing web service (\acr{REST} api) that facilitates video uploads, transcoding and streaming. Coached their development team on system design, Ruby development (using Merb/Rails) and testing strategies such as \acr{TDD}/\acr{BDD}.}}
}

%------------------------------------------------

\begin{center}
\textit{Please refer to \href{http://www.linkedin.com/in/ciesbreijs}{my Linkedin profile} for the complete list of work experiences along with recommendations.}
\end{center}

%------------------------------------------------

\spacedhrule{-0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\roottitle{Education} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Erasmus University Rotterdam}
{\textsc{Rotterdam, The Netherlands}} {

\headedsubsection % Job title entry for the current employer
{Bachelor degree in Computer Science \& Economics}
{2004 -- 2007}
{\bodytext{Focussed on the economics of open source, rapid application development (\acr{RAD}) and the semantic web technology stack (\acr{RDF}/\acr{RDFS}, \acr{OWL} and \acr{SPARQL}).}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Technical University Delft}
{\textsc{Delft, The Netherlands}} {

\headedsubsection % Job title entry for the current employer
{Industrial Design Engineering \textnormal{(discontinued)}}
{2001 -- 2002} {}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Libanon Lyceum}
{\textsc{Rotterdam, The Netherlands}} {

\headedsubsection % Job title entry for the current employer
{\acr{VWO} \textnormal{(pre-university secondary education)}}
{1994 -- 2000} {}
}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Skills} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Technical specialties:}
{Software design and implementation, with(in) a team. I love Ruby/Python/Java/C++ and flirt regularly with Haskell. Solid knowledge of web technologies:\ \acr{HTML+CSS}, \acr{XML}, \acr{RDF}, \acr{REST}, \acr{SOAP} and JavaScript (mainly jQuery). Linux administration skills:\ bash, Apache, My\acr{SQL}, Postgres\acr{SQL}, virtualization/cloud (Open\acr{VZ}, \acr{VM}ware, \acr{KVM}, Xen and \acr{EC}2), datacenter automation (Puppet and Chef), continuous integration (Hudson/Jenkins).}

%------------------------------------------------

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Natural languages:}
{Dutch \textit{(mother tongue)}, English \textit{(full professional proficiency)}, German \textit{(limited working proficiency)}, French \textit{(elementary proficiency)} and Mandarin Chinese \textit{(beginner)}.}

%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Interests} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Non-exhaustive and in alphabetical order:}
{Art, Buddhism, cryptography, music, open source, philosophy, software engineering, travel, typography (e.g.\ graphic design, \LaTeX), \acr{UI}/\acr{UX} and vegetarian cooking.}

%----------------------------------------------------------------------------------------

\end{document}